---
title: "A Priori Consistency"
author: "Emorie D Beck"
date: "02/25/2019"
output:
  html_document:
    number_sections: yes
    theme: united
    highlight: tango
    df_print: paged
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, cache = F)
```

# Workspace  
```{r}
data_path <- "" # this is not needed
wd <- ""
```

## Packages  

```{r}
library(psych)
library(knitr)
library(kableExtra)
library(rstanarm)
library(brms)
library(tidybayes)
library(plyr)
library(tidyverse)
```

## Codebook  
```{r}
(codebook <- sprintf("%s/data/codebook.csv", wd) %>% read_csv())
```


## Data  
### Self Trait Data
```{r, eval = F}
self.trait.codebook <- codebook %>% filter(perspective == "self" & level == "trait")
self.data <- sprintf("%s/data/self/target_w1.csv", wd) %>% read_csv() %>%
  select(one_of(paste(self.trait.codebook$old_name, "w1", sep = "."))) %>%
  setNames(self.trait.codebook$new_name)
write.csv(self.data, file = sprintf("%s/data/self_trait_data.csv", wd), row.names = F)
```

```{r}
(self.trait.data <- sprintf("%s/data/self_trait_data.csv", wd) %>% read_csv)
self.trait.con <- self.trait.data %>%
  select(-contains("BFI")) %>%
  gather(key = item, value = value, contains("consistency"), contains("personality"), na.rm = T) %>%
  separate(item, c("type", "item"), sep = "__") %>%
  spread(type, value) %>%
  mutate(consistency = mapvalues(consistency, 1:4, 4:1))

# self.trait.con <- self.trait.con %>%
#   group_by(proc__SID) %>%
#   summarize_at(vars(consistency, personality), list(~mean), na.rm = T) %>%
#   mutate(item = "all items") %>%
#   ungroup() %>%
#   full_join(self.trait.con) 
```

### Observer Trait Data  
```{r, eval = F}
observer.codebook <- codebook %>% filter(perspective == "observer" & level == "trait")

read_fun <- function(Obs){
  print(Obs)
  cb <- observer.codebook %>% filter(observer == Obs)
  obs.w1 <- sprintf("%s/data/informant/i%s_w1_RENAMED.csv", wd, Obs) %>% read_csv() %>% 
    select(one_of(cb$old_name)) %>%
    setNames(cb$new_name) %>%
    separate(proc__SID, c("proc__SID", "inf"), -2) %>%
    select(-inf)
}

obs.data <- tibble(observer = 1:10) %>%
  mutate(data = map(observer, read_fun)) %>% 
  unnest(data) %>%
  filter(!is.na(proc__SID))

write.csv(obs.data, file = sprintf("%s/data/informant_data.csv", wd), row.names = F)
```

```{r}
(obs.data <- sprintf("%s/data/informant_data.csv", wd) %>% read_csv)
obs.con <- obs.data %>%
  gather(key = item, value = value, -proc__SID, -observer, na.rm = T) %>%
  separate(item, c("type", "item"), sep = "__") %>%
  spread(type, value) %>%
  mutate(consistency = mapvalues(consistency, 1:4, 4:1))

# obs.con <- obs.con %>%
#   group_by(proc__SID, observer) %>%
#   summarize_at(vars(consistency, personality), list(~mean), na.rm = T) %>%
#   mutate(item = "all items") %>%
#   ungroup() %>%
#   full_join(obs.con) 
```

### Self State Data
```{r, eval = F}
state_codebook <- codebook %>% filter(level == "state")

# load and rename wave 1 data
self.state.data <- sprintf("%s/esm_w1_RENAMED.csv", data_path) %>% read_csv() %>%
  select(one_of(paste(state_codebook$old_name, "w1", sep = "."))) %>%
  setNames(state_codebook$new_name) 

vars <- tibble(
  old = c("E_outgoing", "A_kind", "C_reliable", "N_worried", "posEmo", "negEmo",  "happy"),
  new = c("E: Outgoing", "A: Kind", "C: Reliable", "N: Worried", "Positive\nEmotion", "Negative\nEmotion", "Happy")
)

write.csv(self.state.data, file = sprintf("%s/data/self_state_data.csv", wd), row.names = F)
```

```{r}
(self.state.data <- sprintf("%s/data/self_state_data.csv", wd) %>% read_csv)
```


## Create Consistency Variables  
```{r}
# state variability  
self.state.con <- self.state.data %>%
  select(proc__SID:proc__beepvar, contains("personality")) %>%
  gather(key = item, value = pers_value, contains("personality"), na.rm = T) %>%
  mutate(item = str_remove(item, "personality__")) %>%
  group_by(proc__SID, item) %>%
  summarize(sd = sd(pers_value, na.rm = T), 
            sit_item = "all situations", n = n(),
            type = "State Variability") %>%
  ungroup() 

# cross-situational consistency
self.state.con <- self.state.data %>%
  select(proc__SID:proc__beepvar, contains("personality")) %>%
  gather(key = item, value = pers_value, contains("personality"), na.rm = T) %>%
  mutate(item = str_remove(item, "personality__")) %>%
  full_join(self.state.data %>%
  select(proc__SID:proc__beepvar, contains("situation")) %>%
  gather(key = sit_item, value = sit_value, contains("situation"), na.rm = T) %>%
  mutate(sit_item = str_remove(sit_item, "situation__"))) %>%
  filter(sit_value == 1) %>%
  group_by(proc__SID, item, sit_item) %>%
  summarize(pers_value = mean(pers_value, na.rm = T)) %>%
  group_by(proc__SID, item) %>% 
  summarize(sd = sd(pers_value, na.rm = T),
            sit_item = "all situations", n = n(),
            type = "Cross-Situational Consistency") %>%
  ungroup() %>%
  full_join(self.state.con)

# pooling (probably not using)
# self.state.con <- self.state.con %>%
#   group_by(proc__SID, sit_item) %>%
#   mutate(num = (n - 1)*sd^2, den = n - 1) %>%
#   summarize(sd = sqrt(sum(num, na.rm = T)/sum(den, na.rm = T)),
#             item = "all items") %>%
#   ungroup() %>%
#   full_join(self.state.con) %>%
#   select(-n)

# cross-situational contingency consistency
self.state.sit <- self.state.data %>%
  select(proc__SID:proc__beepvar, contains("personality")) %>%
  gather(key = item, value = pers_value, contains("personality"), na.rm = T) %>%
  mutate(item = str_remove(item, "personality__")) %>%
  full_join(self.state.data %>%
  select(proc__SID:proc__beepvar, contains("situation")) %>%
  gather(key = sit_item, value = sit_value, contains("situation"), na.rm = T) %>%
  mutate(sit_item = str_remove(sit_item, "situation__"))) %>%
  filter(sit_value == 1) %>%
  group_by(proc__SID, sit_item, item) %>%
  filter(sd(pers_value, na.rm = T) != 0) %>%
  summarize(n = n(), sd = sd(pers_value, na.rm = T),
            type = "Behavioral Signature Consistency") %>%
  ungroup() 

(self.state.con.all <- self.state.sit %>% 
  full_join(self.state.con))
```

```{r}
self.state.con.all %>%
  filter(item %in% vars$old) %>%
  group_by(sit_item, item, type) %>%
  mutate_at(vars(sd), funs(mean, sd), na.rm = T) %>%
  ggplot(aes(x = sd, y = sit_item, fill = item)) +
    geom_halfeyeh() +
    facet_grid(type~item, scales = "free_y", space = "free_y") +
    theme_classic()
```

# Zero-Order Relationships  
```{r}
self.trait.con %>% mutate(perspective = "self") %>%
  full_join(obs.con %>% mutate(proc__SID = as.numeric(proc__SID), perspective = "observer")) %>%
  select(proc__SID, item, consistency, perspective) %>%
  group_by(item, proc__SID, perspective) %>% 
  summarize(consistency = mean(consistency, na.rm = T)) %>%
  spread(perspective, consistency) %>%
  group_by(item) %>%
  summarize(r = cor(self, observer, use = "pairwise"))
```


# Relationship Between A Priori Consistency and Observed Consistency  
```{r}
r_fun <- function(df, rownum){
  if(rownum == 1){fit}
  else{tmp <- update(fit, newdata = df)}
}

consistency_nested <- self.trait.con %>% mutate(perspective = "self") %>%
  full_join(obs.con %>% mutate(proc__SID = as.numeric(proc__SID), perspective = "observer")) %>%
  full_join(self.state.con.all) %>%
  filter(!is.na(item)) %>%
  group_by(proc__SID, perspective, item, sit_item, type) %>%
  summarize_at(vars(consistency, sd), list(mean), na.rm = T) %>%
  group_by(perspective, item, sit_item, type) %>%
  mutate_at(vars(consistency, sd), funs(z = as.numeric(scale(.)))) %>%
  # filter(n() >= 20) %>%
  nest() %>%
  rownames_to_column() %>%
  drop_na() 

fit <- brm(consistency_z ~ sd_z, data = consistency_nested$data[[1]])

consistency_nested <- consistency_nested %>%
  mutate(r = map2(data, rowname, r_fun),
         tidy = map(r, broom::tidy),
         samples = map(r, ~gather_draws(., b_sd_z)))

res <- consistency_nested %>%
  unnest(tidy) %>%
  filter(term == "b_sd_z") %>%
  # filter(sign(lower) == sign(upper)) %>%
  arrange(type) %>%
  group_by(perspective, type, item) %>%
  mutate_at(vars(estimate, lower, upper), list(fisherz)) %>%
  summarise_at(vars(estimate, lower, upper), list(mean)) %>%
  mutate_at(vars(estimate, lower, upper), list(fisherz2r)) 
  
res %>% 
  mutate(sig = ifelse(sign(lower) == sign(upper), "sig", "ns")) %>%
  mutate_at(vars(estimate:upper), list(~sprintf("%.2f", .))) %>%
  mutate(CI = sprintf("[%s, %s]", lower, upper)) %>%
  mutate_at(vars(estimate, CI), list(~ifelse(sig == "sig", sprintf("<strong>%s</strong>", .), .))) %>%
  select(perspective:item, b = estimate, CI) %>%
  gather(key = est, value = value, b, CI) %>%
  unite(tmp, type, est, sep = ".") %>%
  spread(key = tmp, value = value)
```

## Cross-Situational Differences 
```{r}
consistency_nested %>%
  unnest(samples) %>%
  filter(type == "Behavioral Signature Consistency" & perspective == "observer") %>%
  ggplot(aes(x = .value, y = sit_item, fill = sit_item)) +
    geom_halfeyeh() +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    facet_grid(~item) +
    theme_classic() +
    theme(legend.position = "none")
```


```{r}
draws_long <- consistency_nested %>%
  unnest(samples) %>%
  group_by(perspective, type, item, .draw) %>%
  summarize(.value = fisherz2r(mean(fisherz(.value), na.rm = T))) %>% 
  group_by(perspective, type, item) %>%
  mutate(m_qi = list(mean_qi(.value))) %>%
  unnest(m_qi) %>%
  ungroup() %>%
  mutate(perspective = str_to_title(perspective),
         sig = ifelse(sign(ymin) == sign(ymax), "sig", "ns"))
```

```{r}
vars <- tibble(
  old = c("E_outgoing", "A_kind", "C_reliable", "N_worried", "posEmo", "negEmo",  "happy"),
  new = c("E: Outgoing", "A: Kind", "C: Reliable", "N: Worried", "Positive\nEmotion", "Negative\nEmotion", "Happy")
)

draws_long %>%
  select(perspective:item, b = y, lower = ymin, upper = ymax, sig) %>%
  distinct() %>%
  mutate_at(vars(b:upper), list(~sprintf("%.2f", .))) %>%
  mutate(CI = sprintf("[%s, %s]", lower, upper),
         item = mapvalues(item, from = vars$old, to = vars$new),
         item = factor(item, levels = vars$new)) %>%
  mutate_at(vars(b, CI), list(~ifelse(sig == "sig", sprintf("<strong>%s</strong>", .), .))) %>%
  select(perspective:item, b, CI) %>%
  gather(key = est, value = value, b, CI) %>%
  unite(tmp, type, est, sep = ".") %>%
  spread(key = tmp, value = value)
```


```{r}
draws_long %>%
  filter(perspective == "Observer") %>%
  mutate(item = mapvalues(item, from = vars$old, to = vars$new),
         item = factor(item, levels = rev(vars$new)),
         type = str_wrap(type, 20)) %>%
  ggplot(aes(x = .value, y = item, fill = sig)) +
    geom_halfeyeh() +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    scale_fill_manual(values = c("lightgrey", "lightgoldenrod2")) +
    scale_x_continuous(limits = c(-.5, .5), breaks = seq(-.5, .5, .25)) +
    labs(x = "r", y = NULL) +
    facet_grid(perspective ~ type) +
    theme_classic() +
    theme(legend.position = "none",
          strip.text = element_text(face = "bold", size = rel(1.2), color = "white"),
          strip.background = element_rect(fill = "black"),
          axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)))
 ggsave(file = sprintf("%s/results/plots/observer_results.png", wd), width = 9, height = 6)

draws_long %>%
  filter(perspective == "Self") %>%
  mutate(item = mapvalues(item, from = vars$old, to = vars$new),
         item = factor(item, levels = rev(vars$new)),
         type = str_wrap(type, 20)) %>%
  ggplot(aes(x = .value, y = item, fill = sig)) +
    geom_halfeyeh() +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    scale_fill_manual(values = c("lightgrey", "lightgoldenrod2")) +
    labs(x = "r", y = NULL) +
    facet_grid(perspective ~ type) +
    theme_classic() +
    theme(legend.position = "none",
          strip.text = element_text(face = "bold", size = rel(1.2), color = "white"),
          strip.background = element_rect(fill = "black"),
          axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)))
ggsave(file = sprintf("%s/results/plots/self_results.png", wd), width = 9, height = 6)
```

## Cross-Rater Comparisons
```{r}
r_fun <- function(df){
  r <- df %>% select(-proc__SID) %>% cor(., use = "pairwise")
  r[upper.tri(r, diag = T)] <- NA
  r_long <- r %>% data.frame %>%
    rownames_to_column("V1") %>%
    gather(key = V2, value = value, -V1, na.rm = T)
  res <- r.test(n = nrow(df), 
                r12 = r_long$value[1], 
                r13 = r_long$value[2], 
                r23 = r_long$value[3])
  tibble(t = res$t, p = res$p)
}

# relationship between consistency measures  
r_obs_comp <- self.trait.con %>% mutate(perspective = "self") %>%
  full_join(obs.con %>% mutate(proc__SID = as.numeric(proc__SID), perspective = "observer")) %>%
  full_join(self.state.con.all) %>%
  mutate(type = str_replace_all(type, " ", "_")) %>%
  filter(!is.na(item) & !is.na(perspective)) %>%
  group_by(proc__SID, perspective, item, sit_item, type) %>%
  summarize_at(vars(consistency, sd), list(mean), na.rm = T) %>%
  ungroup() %>%
  spread(key = perspective, value = consistency) %>%
  group_by(item, sit_item, type) %>%
  nest() %>%
  mutate(r = map(data, r_fun)) 

r_obs_comp %>%
  unnest(r, .drop = T) %>%
  filter(p < .05)
```

# Presentation Figures  

## Nomothetic Distributions  
```{r}
data(bfi)

bfi %>%
  rownames_to_column("SID") %>%
  gather(key = item, value = value, A1:O5, na.rm = T) %>%
  separate(item, c("trait", "item"), -1) %>%
  mutate(trait = factor(trait, levels = c("E", "A", "C", "N", "O"))) %>%
  group_by(SID, age, gender, trait) %>%
  summarize(value = mean(value, na.rm = T)) %>%
  ggplot(aes(x = value, y = 1, fill = trait)) +
  geom_halfeyeh() +
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) +
  scale_fill_manual(values = c("blue", "orange2", "goldenrod1", "springgreen3", "purple3")) +
  labs(x = NULL, y = NULL, title = "") +
  facet_grid(~trait, scales = "free_y") +
  theme_classic() +
  theme(legend.position = "none",
        axis.title = element_text(face = "bold", size = rel(1.2)),
        axis.text.x = element_text(face = "bold", size = rel(1.2)),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank())
ggsave(sprintf("%s/results/plots/nomo_dist.png", wd), width = 8, height = 1.75)
```

## Idiographic Distributions  
```{r}
load(sprintf("%s/results/sample_data.RData", wd))

s.bfi.mi <- BFI.mi %>%
  gather(key = item, value = value, A_Cmpn:O_IntCur, na.rm = T) %>%
  separate(item, c("trait", "item"), sep = "_") %>%
  group_by(SID, all_beeps, trait) %>%
  summarize(value = mean(value, na.rm = T)) %>%
  ungroup() %>%
  mutate(trait = factor(trait, levels = c("E", "A", "C", "N", "O")))

draw.a.plot <- function(sid){
  s.bfi.mi %>% filter(SID == sid) %>%
    group_by(trait) %>% 
    mutate(sd = sd(value, na.rm = T), m = mean(value, na.rm = T)) %>%
    ungroup() %>%
    ggplot(aes(x = value, y = 1, fill = trait)) +
    geom_halfeyeh() +
    geom_text(aes(label = sprintf("%.2f", sd), y = 1.15, x = m), color = "white") +
    scale_x_continuous(limits = c(1,5), breaks = seq(1,5,1)) +
    scale_fill_manual(values = c("blue", "orange2", "goldenrod1", "springgreen3", "purple3")) +
    labs(x = NULL, y = NULL, title = sid) +
    facet_grid(~trait, scales = "free_y") +
    theme_classic() +
    theme(legend.position = "none",
          axis.title = element_text(face = "bold", size = rel(1.2)),
          axis.text.x = element_text(face = "bold", size = rel(1.2)),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.title = element_text(hjust = .5))
}

library(animation)

loop.animate <- function() {
    lapply(unique(s.bfi.mi$SID), function(i) {
        print(draw.a.plot(i))
    })
}

# create GIF of all edges
saveGIF(loop.animate(), interval = .5, movie.name="idio_dist.gif", ani.width = 500, ani.height = 109.375,
        imgdir = sprintf("%s/results/plots", wd))

draw.a.plot(102204)
ggsave(sprintf("%s/results/plots/idio_dist_102204.png", wd), width = 8, height = 1.75)

draw.a.plot(102902)
ggsave(sprintf("%s/results/plots/idio_dist_102902.png", wd), width = 8, height = 1.75)
```

## If...then Profiles of averages 
```{r}
sits <- c("class", "studied", "video", "passFacebook", "music", "actFacebook")
self.state.prof <- self.state.data %>%
  select(proc__SID:proc__beepvar, contains("personality")) %>%
  gather(key = item, value = pers_value, contains("personality"), na.rm = T) %>%
  mutate(item = str_remove(item, "personality__")) %>%
  full_join(self.state.data %>%
  select(proc__SID:proc__beepvar, contains("situation")) %>%
  gather(key = sit_item, value = sit_value, contains("situation"), na.rm = T) %>%
  mutate(sit_item = str_remove(sit_item, "situation__"))) %>%
  filter(sit_value == 1) %>%
  group_by(proc__SID, item, sit_item) %>%
  summarize(pers_value = mean(pers_value, na.rm = T)) %>% 
  filter(sit_item %in% sits) %>%
  group_by(proc__SID, item) %>%
  filter(n() == 6) %>%
  # group_by(proc__SID, sit_item) %>%
  # filter(grepl("E_", item)) %>%
  ungroup()

draw.a.plot <- function(sid){
  df <- self.state.prof %>%
    filter(proc__SID == sid & grepl("E_outgoing", item))
  df <- df %>% group_by(proc__SID, item) %>% 
    summarize(pers_value = mean(pers_value, na.rm = T), sit_item = "Overall", type = "Overall") %>%
    full_join(df %>% mutate(type = "Situation-Specific")) 
  sum.df <- df %>% filter(sit_item != "Overall") %>% mutate(sit_item = "Overall", type = "Overall")
  p <- df %>%
    ggplot(aes(y = sit_item, x = pers_value, color = item, group = item)) +
      scale_color_manual(values = c("blue", "springgreen3")) +
      scale_x_continuous(limits = c(1,5), breaks = seq(1,5,1)) +
      # geom_line(size = 1) +
      geom_path() +
      geom_density_ridges(data = sum.df, aes(y = sit_item, x = pers_value), color = NA, fill = "springgreen3", panel_scaling = F) +
      geom_point(color = "black", size = 2) +
      coord_flip()+
      labs(y = NULL, x = "Average State Rating", color = NULL, title = sid) +
      facet_grid(~type,  scales = "free_x", space = "free") +
      theme_classic() +
      theme(legend.position = "none",
            axis.text.x = element_text(face = "bold", size = rel(1), angle = 35, hjust = 1),
            axis.text.y = element_text(face = "bold", size = rel(1.2)),
            plot.title = element_text(hjust = .5),
            strip.background = element_rect(fill = "black"),
            strip.text = element_text(color = "white", size = rel(1.2), face = "bold")) 
    pt <- ggplot_gtable(ggplot_build(p))
    pt$widths[5] = unit(10/5.5, units = "null")
    pt$widths[7] = unit(10-10/5.5, units = "null")
    pt
}

loop.animate <- function() {
    lapply(unique(self.state.prof$proc__SID)[1:50], function(i) {
        grid.newpage()
        grid.draw(draw.a.plot(i))
    })
}

# create GIF of all edges
saveGIF(loop.animate(), interval = .5, movie.name="idio_profile.gif", ani.width = 325, ani.height = 200,
        imgdir = sprintf("%s/results/plots", wd))
```


## If...then Profiles of variability  
```{r}
self.state.long <- self.state.data %>%
  select(proc__SID:proc__beepvar, contains("personality")) %>%
  gather(key = item, value = pers_value, contains("personality"), na.rm = T) %>%
  mutate(item = str_remove(item, "personality__")) %>%
  full_join(self.state.data %>%
  select(proc__SID:proc__beepvar, contains("situation")) %>%
  gather(key = sit_item, value = sit_value, contains("situation"), na.rm = T) %>%
  mutate(sit_item = str_remove(sit_item, "situation__"))) %>%
  filter(sit_value == 1 & proc__SID %in% unique(self.state.prof$proc__SID)) %>% 
  group_by(proc__SID, item, sit_item) %>%
  mutate(m_pers_value = mean(pers_value, na.rm = T)) %>% 
  ungroup() %>%
  filter(sit_item %in% sits) %>%
  group_by(proc__SID, sit_item, item) %>%
  mutate(n = n()) %>%
  group_by(proc__SID) %>%
  filter(all(n > 1)) %>% 
  ungroup() %>%
  arrange(proc__SID)

draw.a.plot <- function(sid){
  df <- self.state.long %>%
    filter(proc__SID == sid & grepl("E_outgoing", item))
  df %>% group_by(proc__SID, item, proc__beepvar) %>% 
    summarize(pers_value = mean(pers_value, na.rm = T), sit_item = "Overall", type = "Overall") %>%
    full_join(df %>% mutate(type = "Situation-Specific")) %>%
    ggplot(aes(y = sit_item, x = pers_value, fill = sit_item)) +
      # scale_fill_manual(values = c("blue", "springgreen3")) +
      scale_x_continuous(limits = c(1,5), breaks = seq(1,5,1)) +
      geom_halfeyeh(alpha = .5) +
      geom_line(size = 1) +
      coord_flip() +
      labs(y = NULL, x = "Average State Rating", color = NULL, title = sid) +
      facet_grid(~type,  scales = "free_x", space = "free") +
      theme_classic() +
      theme(legend.position = "none",
            axis.text.x = element_text(face = "bold", size = rel(1), angle = 35, hjust = 1),
            axis.text.y = element_text(face = "bold", size = rel(1.2)),
            plot.title = element_text(hjust = .5),
            strip.background = element_rect(fill = "black"),
            strip.text = element_text(color = "white", size = rel(1.2), face = "bold")) 
}

loop.animate <- function() {
    lapply(unique(self.state.long$proc__SID)[1:50], function(i) {
        print(draw.a.plot(i))
    })
}

# create GIF of all edges
saveGIF(loop.animate(), interval = .5, movie.name="idio_profile_var.gif", ani.width = 325, ani.height = 200,
        imgdir = sprintf("%s/results/plots", wd))
```

